Epidemic Tracking and Forecasting: Lessons Learned from a Tumultuous Year

### 2021-12-01 perspective/paper.tex
Fix typo

In the \emph{interpandemic phase}, the main activity is threat scanning for
threats, namely monitoring data streams and events throughout the world for
disconcerting developments.  Relevant statistical tools include anomaly
detection and scan statistics to help decide when an epidemiological
investigation is warranted.  While it may be possible to rank the risks of
different outbreak triggering events (like species jumping or point mutations)
in different locations, which could in turn be used to inform surveillance
resource allocation, conventional forecasting has a limited role to play in this
phase, as such events have large inherent uncertainty.

>>>>

In the \emph{interpandemic phase}, the main activity is scanning for
threats, namely monitoring data streams and events throughout the world for
disconcerting developments.  Relevant statistical tools include anomaly
detection and scan statistics to help decide when an epidemiological
investigation is warranted.  While it may be possible to rank the risks of
different outbreak triggering events (like species jumping or point mutations)
in different locations, which could in turn be used to inform surveillance
resource allocation, conventional forecasting has a limited role to play in this
phase, as such events have large inherent uncertainty.
